%!TEX root = ../report.tex
\chapter{Context}\label{ch:context}
In this chapter we will discuss the context of the Trale project sequence.

The Trale project sequence is being carried out in the \ac{sofa} module at Fontys Venlo.
The idea of this module is to simulate an authentic software project as you would carry out in your professional career
as Software Engineer.
The authentic part in that comes from the fact that you have to collaborate in a somewhat bigger project for a real
world customer, with the lecturers as your guidance.
The goal which this module aims to achieve is that you will be ready for your bachelor thesis and have had a final
rehearsal before the real deal.
As this year \ac{sofa} project is early in the Trale project life cycle, we had to do a lot of analysis and research in
order to make things work.

When the \ac{sofa} module comes to a close, the Trale project has quite a few deliverables to produce regarding the
project sequence:

\begin{itemize}
    \item Group dossier(this document)
    \item Personal development plan
    \item Pitch video
    \item Handover document
    \item Peer review
\end{itemize}

All these deliverables are geared towards making a student aware of their role in a software development team, and how
to plan for self-improvement.
Subsequently, the pitch video, handover document and peer review teaches you valuable real world skills in terms of
reviewing your team members, presenting your project in a professional and convincing manner.
Finally, you can deliver the project to next years' development team in an understandable and professional manner using
the handover document

Taking all of this into account it makes sense to use a real world project with real world complexity such as Trale
for a module that aims to test many skills.
Do note that the benefits go both ways: not only do the project members learn a lot from developing this project in
this setting, but it is very good for the project's health as well.
This is made possible by lecturer meetings which encourages best practices being upheld when working on a project of
this scale.
